Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-23 paper-v1.tex
remove listing 1.1

\input{solidity-highlighting.tex}

@@

\subsubsection{Tokenomics}
AntsReview integrates few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS, is the primary protocol token and can be staked into an AntReview.
\newline ANTS [see \ref{lst:code}] is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.

\begin{lstlisting}[caption={ANTS.sol},label={lst:code},language=Solidity]
/// SPDX-License-Identifier: GPL-3.0
pragma solidity 0.6.8;

///@title Ants-Review
///@author Nazzareno Massari
///@notice ANTS ERC20 Token
///@dev All function calls are currently implemented without side effects through TDD approach
///@dev OpenZeppelin library is used for secure contract development

import "@openzeppelin/contracts/access/Ownable.sol";
import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";

contract ANTS is Ownable, ERC20PresetMinterPauser {

  constructor()
  ERC20PresetMinterPauser("Ants-Review", "ANTS")
  public {

  }

}
\end{lstlisting}

>>>>

@@

\subsubsection{Tokenomics}
AntsReview integrates few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS, is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
